Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-03-28 manuscript.Rmd
updated ignore for LFS

Three online repositories contain openly shared data, materials, and analysis code. A Databrary repository (https://nyu.databrary.org/volume/1580) includes an exemplar participant's recording session, with the raw video data files, the Datavyu annotations of those video files, a log file with machine-readable synchronization points and nap/diaper change times, and accelerometer and gyroscope data for each of the 4 sensors. A CodeOcean capsule (LINK) hosts an R environment with the exemplar participant's data and source code to: 1) synchronize IMU and video annotations, 2) calculate windowed motion features for their data, and 3) train and test the body position classifier using an "individual model". The chosen participant's classification accuracy was at the median level. Because of the overall size of the full dataset and the computational power/time required to synchronize and create windowed datasets for each session, it would not be feasible to create a reproducible environment to process all 34 sessions. However, in a second CodeOcean capsule (LINK) we share the entire result: The dataset of windowed motion features with corresponding body position codes used to validate the method (described in the results below), along with the processed intermediary files used for each set of analyses. This reproducible manuscript created in *papaja* [@papaja] can be executed in the CodeOcean environment for full computational transparency, and can be downloaded from Github (LINK).
<!-- FINAL LINKS -->

>>>>

Three online repositories contain openly shared data, materials, and analysis code. A Databrary repository (https://nyu.databrary.org/volume/1580) includes an exemplar participant's recording session, with the raw video data files, the Datavyu annotations of those video files, a log file with machine-readable synchronization points and nap/diaper change times, and accelerometer and gyroscope data for each of the 4 sensors. A GitHub repository (LINK) contains the exemplar participant's data and source code to: 1) synchronize IMU and video annotations, 2) calculate windowed motion features for their data, and 3) train and test the body position classifier using an "individual model". The chosen participant's classification accuracy was at the median level. Because of the overall size of the full dataset and the computational power/time required to synchronize and create windowed datasets for each session, it would not be feasible to reproduce the calculations for all 34 sessions. However, in a second Github repository (LINK) we share the full results of those computations: The dataset of windowed motion features with corresponding body position codes used to validate the method (described in the results below), along with the processed intermediary files used for each set of analyses. This reproducible manuscript created in RMarkdown and *papaja* [@papaja] is generated from those data files for computational transparency.
<!-- FINAL LINKS -->
